


```{r}
loadout<-FALSE 
source("_R/1_global.R")  	
source("_R/2_functions.R")  
source("_R/3_load.R")     
source("_R/4_clean.R" )
source("_R/5_tables.R") 
source("_R/6_figures.R") 
source("_R/7_model.R")
#source("_R/8_analysis.R")
```

## number of repeats

table(dat$tag)
dat$doy<-as.numeric(
dat$tmp<-1
xx<-dcast(dat,tag~date,value.var="tmp",sum)
zz<-apply(xx[,-1],1,paste,collapse="")
zz[grep(zz,"11")]


## Model fit and estimates for top model


```{r}
ni<-75*500
nb<-30*500
#######################################################################
#
#  MODEL 3: TEMPERATURE AND STAGE WITH PREDICTIONS AND HABITAT SELECTION
#
#######################################################################
params<- c("beta1",'beta2','Intercept',
	'Beta_stage','Beta_temp','p',"sel") 
stages<- scale(seq(-2,18,by=2),stage_mn,stage_sd)   
temps<-scale(seq(5,38,by=5),temp_mn,temp_sd)
selection<- expand.grid(temp=temps,stage=0,loc=c(1,2))
selection<- rbind(selection,expand.grid(temp=0,stage=stages,loc=c(1,2)))
mod_dat2<- mod_dat
mod_dat2$n_sel<- nrow(selection)
mod_dat2$select<- selection
inits<-function(){
    list('beta1'=matrix(c(NA,NA,runif(2*6)),2,7,byrow=FALSE),
	'beta2'=matrix(c(NA,NA,runif(2*6)),2,7,byrow=FALSE),
	'Intercept'=matrix(c(NA,NA,runif(2*6)),2,7,byrow=FALSE),
	'Beta_stage'=matrix(c(NA,NA,runif(2*6)),2,7,byrow=FALSE),
	'Beta_temp'=matrix(c(NA,NA,runif(2*6)),2,7,byrow=FALSE))
   }
out <- jags(data=mod_dat2,
	inits=inits,
	parameters=params,	
	model.file=mod_03_gof,
	n.chains = 3,	
	n.iter = ni,n.burnin = nb,     
	n.thin=2,
	working.directory=getwd())
save(out, file="_output/out-model-03-gof.Rdata")

```

## manuscript figures.
png(file = "_figures/figure-02.png", bg = "transparent", type = c("cairo"), width=2000, height=2000, res=300)
figures(2)
dev.off()

png(file = "_figures/figure-03.png", bg = "transparent", type = c("cairo"), width=2000, height=2000, res=300)
figures(3)
dev.off()

png(file = "_figures/figure-04.png", bg = "transparent", type = c("cairo"), width=2000, height=2000, res=300)
figures(4)
dev.off()


png(file = "_figures/figure-05.png", bg = "transparent", type = c("cairo"), width=2000, height=2000, res=300)
figures(5)
dev.off()

png(file = "_figures/figure-06.png", bg = "transparent", type = c("cairo"), width=2000, height=2000, res=300)
figures(6)
dev.off()


png(file = "_figures/figure-S1.png", bg = "transparent", type = c("cairo"), width=2000, height=2000, res=300)
figures("S1")
dev.off()

png(file = "_figures/figure-S2.png", bg = "transparent", type = c("cairo"), width=2000, height=2000, res=300)
figures("S2")
dev.off()



# Tables Deviance information criteria (DIC) values and model 
# selection results for candidate habitat selection models for 
# Pallid Sturgeon captures in the Lower Mississippi River. 

```{r, echo=FALSE,warnings=FALSE, message=FALSE}
tbl1<- tables(1)
kable(tbl1,digits=2,caption = NULL,row.names=FALSE)
```
