


```{r}
source("_R/1_global.R")  	
source("_R/2_functions.R")  
loadout<-TRUE       
source("_R/3_load.R")     
source("_R/4_clean.R" )
source("_R/5_tables.R") 
source("_R/6_figures.R") 
source("_R/7_model.R")
```
## number of repeats

table(dat$tag)
dat$doy<-as.numeric(
dat$tmp<-1
xx<-dcast(dat,tag~date,value.var="tmp",sum)
zz<-apply(xx[,-1],1,paste,collapse="")
zz[grep(zz,"11")]

## manuscript figures.
png(file = "_figures/figure-02.png", bg = "transparent", type = c("cairo"), width=2000, height=2000, res=300)
figures(2)
dev.off()

png(file = "_figures/figure-03.png", bg = "transparent", type = c("cairo"), width=2000, height=2000, res=300)
figures(3)
dev.off()

png(file = "_figures/figure-04.png", bg = "transparent", type = c("cairo"), width=2000, height=2000, res=300)
figures(4)
dev.off()


png(file = "_figures/figure-05.png", bg = "transparent", type = c("cairo"), width=2000, height=2000, res=300)
figures(5)
dev.off()

png(file = "_figures/figure-06.png", bg = "transparent", type = c("cairo"), width=2000, height=2000, res=300)
figures(6)
dev.off()


png(file = "_figures/figure-S1.png", bg = "transparent", type = c("cairo"), width=2000, height=2000, res=300)
figures("S1")
dev.off()

png(file = "_figures/figure-S2.png", bg = "transparent", type = c("cairo"), width=2000, height=2000, res=300)
figures("S2")
dev.off()



# Tables Deviance information criteria (DIC) values and model 
# selection results for candidate habitat selection models for 
# Pallid Sturgeon captures in the Lower Mississippi River. 

```{r, echo=FALSE,warnings=FALSE, message=FALSE}
tbl1<- tables(1)
kable(tbl1,digits=2,caption = NULL,row.names=FALSE)
```
