

```{r,echo=FALSE,warnings=FALSE, message=FALSE}
setwd("C:/Users/mcolvin/Documents/projects/MS-Pallid-Habitat-Selection/analysis")
	source("./src/1_global.R")  	
	source("./src/2_functions.R")         
	source("./src/3_load.R")     
  	source("./src/4_clean.R" )
 	source("./src/5_tables.R") 
	source("./src/6_figures.R") 
	source("./src/7_model.R")
```

# Tables

Table 1. Deviance information criteria (DIC) values and model 
selection results for candidate habitat selection models for 
Pallid Sturgeon captures in the Lower Mississippi River. 

```{r, echo=FALSE,warnings=FALSE, message=FALSE}
tbl1<- tables(1)
kable(tbl1,digits=2,caption = NULL,row.names=FALSE)
```

# Figures

```{r, echo=FALSE,dpi=600,fig.cap=""}
figures(1)
```

Figure 1.  Lower Mississippi River temperature and 
stage over the study period for Catfish Point river segment.



```{r, echo=FALSE,dpi=600,fig.cap=""}
figures(2)
```

Figure 2.  Lower Mississippi River temperature and 
stage over the study period for Tara to Vicksburg 
river segment.



```{r, echo=FALSE,dpi=600,fig.cap=""}
figures(4)
```
  
Figure 3.  Predicted habitat availability at varying river 
stages for Catfish Point (top panel) and Tara to Vicksburg 
(bottom panel) segments of the lower Mississippi River.  

```{r, echo=FALSE,dpi=600,fig.cap=""}
figures(5)
```

Figure 4. Predicted probability of habitat use at 
varying river temperature with river stage held at average.
Predicted values for the Mississippi River segment located at Catfish Point.
Top panel represents actual probabilities of use and bottom panel represents 
cumlative probabilities.


```{r, echo=FALSE,dpi=600,fig.cap=""}
figures(6)
```

Figure 4.  Predicted probability of habitat use at 
varying river stage with river temperature held at average.
Predicted values for the Mississippi River segment located at Catfish Point.
Top panel represents actual probabilities of use and bottom panel represents 
cumlative probabilities.  


```{r, echo=FALSE,dpi=600,fig.cap=""}
figures(8)
```

Figure 5.  Predicted probability of habitat use at 
varying river temperature with river stage held at average.
Predicted values for the Mississippi River segment from Tara to Vicksburg.
Top panel represents actual probabilities of use and bottom panel represents 
cumlative probabilities. 




```{r, echo=FALSE,dpi=600,fig.cap=""}
figures(7)
```

Figure 6. Predicted probability of habitat use at 
varying river stage with river temperature held at average.
Predicted values for the Mississippi River segment from Tara to Vicksburg.
Top panel represents actual probabilities of use and bottom panel represents 
cumlative probabilities.

